Autocorrelation in Sparse Distributed Memory

### 2018-09-20 paperIEEE.tex
minor

 \usepackage[round]{natbib}

@@

OpenCL
python (show example with figure)
Technical Documentation

@@

\begin{IEEEbiography}[{\fbox{\begin{minipage}[t][1.25in]{1in}%
Replace this box by an image with a width of 1\,in and a height of
1.25\,in!%
\end{minipage}}}]{Your Name}
 All about you and the what your interests are.
\end{IEEEbiography}

\begin{IEEEbiographynophoto}{Coauthor}
Same again for the co-author, but without photo
\end{IEEEbiographynophoto}

>>>>

 \usepackage[round, numbers]{natbib}

@@

OpenCL for the partial binomail sum (cite `Inference-Based Similarity Search in Randomized Montgomery Domains for Privacy-Preserving Biometric Identification')
python (show example with figure)
Technical Documentation

@@

\begin{IEEEbiography}[{\fbox{\begin{minipage}[t][1.25in]{1in}%
Replace this box by an image with a width of 1\,in and a height of
1.25\,in!%
\end{minipage}}}]{Marcelo Salhab Brogliato} received the Ph.D. degree from Getulio Vargas Foundation in 2018. Vialink, sdm.ai,
\end{IEEEbiography}

\begin{IEEEbiography}[{\fbox{\begin{minipage}[t][1.25in]{1in}%
Replace this box by an image with a width of 1\,in and a height of
1.25\,in!%
\end{minipage}}}]{Alexandre Linhares} received the Ph.D. degree from the National Institute of Space Research, 2001. He is an Associate Professor at the Center of Behavioral Research, EBAPE / Getulio Vargas Foundation.  He has published circa 30 papers in journals such as \emph{Artificial Intelligence, Biological Cybernetics, Cognitive Science, IEEE Transactions on Evolutionary Computation, Information Sciences, Frontiers in Psychology,} etc.
\end{IEEEbiography}
